\huge The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-05-11 Writeup/kohler_clarke_2021.tex
Fixed 63 - 64 mistake in fig4 caption

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{This plot shows the proportion of subgroup relationships that satisfy $p(\Delta >0 | data) > x$. We can see that if we take $x = 0.95$ as our threshold, the subgroup relationships are preserved in 56/63 = 89\% and 49/64 = 78\% of the comparisons for the primary SSVEP and threshold duration datasets, repectively. This compares to the 32/64= 50\% and 22/64 = 35\% for the SSVEP control datasets.}
\label{fig:durations_rotations}
\end{figure}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{This plot shows the proportion of subgroup relationships that satisfy $p(\Delta >0 | data) > x$. We can see that if we take $x = 0.95$ as our threshold, the subgroup relationships are preserved in 56/63 = 89\% and \textcolor{ForestGreen}{48/63 = 76\%} of the comparisons for the primary SSVEP and threshold duration datasets, receptively. This compares to the \textcolor{ForestGreen}{32/63= 51\%} and \textcolor{ForestGreen}{22/63 = 35\%} for the SSVEP control datasets.}
\label{fig:durations_rotations}
\end{figure}
